ASAH1 rGBM Manuscript ELISA Figure

### 2023-02-06 results/elisa_plasma_proteomics/manuscript_elisa_figure_analysis.Rmd
[ADD] finalized ELISA plots, pngs and svgs, and add cox-ph model

## All 4
fit <- survfit(Surv(Time.to.reccurence..days., status) ~ ASAH1 + SYNM + GPNMB + MMP9, data = ttr_surv_data)
print(fit)
# Change color, linetype by strata, risk.table color by strata
ttr_surv_p5 <- ggsurvplot(fit,
          pval = TRUE, pval.coord = c(650, 0.85), conf.int = F,
          risk.table = FALSE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          legend.title = "",
          legend.labs = c(
            sprintf("ASAH1=high, SYNM=high, GPNMB=high, MMP9=high (n=1)"), 
            sprintf("ASAH1=high, SYNM=low, GPNMB=high, MMP9=low (n=1)"),  
            sprintf("ASAH1=low, SYNM=high, GPNMB=low , MMP9=high (n=2)"), 
            sprintf("ASAH1=high, SYNM=high, GPNMB=low , MMP9=low (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=high, MMP9=low (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=low , MMP9=high (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=low , MMP9=low (n=2)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=high, MMP9=high (n=1)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=high, MMP9=low (n=1)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=low , MMP9=high (n=2)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=high, MMP9=low (n=3)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=low , MMP9=high (n=1)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=low , MMP9=low (n=2)")
            )
          ) +
  labs(x="Time to Recurrence (Days)", y="Time to Recurrence probability")  +
  guides(col=guide_legend(nrow=4,byrow=TRUE))

@@

## COXPH
fit <- coxph(Surv(Time.to.reccurence..days., status) ~ sex + ASAH1.ng.ml + SYNM.ng.ml + GPNMB.ng.ml + MMP.9.ng.ml, data = ttr_surv_data)
print(summary(fit))

>>>>

## All 4 ----
fit <- survfit(Surv(Time.to.reccurence..days., status) ~ ASAH1 + SYNM + GPNMB + MMP9, data = ttr_surv_data)
print(fit)
# Change color, linetype by strata, risk.table color by strata
ttr_surv_p5 <- ggsurvplot(fit,
          pval = TRUE, pval.coord = c(650, 0.85), conf.int = F,
          risk.table = FALSE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          legend.title = "",
          legend.labs = c(
            sprintf("ASAH1=high, SYNM=high, GPNMB=high, MMP9=high (n=1)"), 
            sprintf("ASAH1=high, SYNM=low, GPNMB=high, MMP9=low (n=1)"),  
            sprintf("ASAH1=low, SYNM=high, GPNMB=low , MMP9=high (n=2)"), 
            sprintf("ASAH1=high, SYNM=high, GPNMB=low , MMP9=low (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=high, MMP9=low (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=low , MMP9=high (n=1)"),
            sprintf("ASAH1=high, SYNM=low , GPNMB=low , MMP9=low (n=2)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=high, MMP9=high (n=1)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=high, MMP9=low (n=1)"),
            sprintf("ASAH1=low, SYNM=high, GPNMB=low , MMP9=high (n=2)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=high, MMP9=low (n=3)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=low , MMP9=high (n=1)"),
            sprintf("ASAH1=low, SYNM=low , GPNMB=low , MMP9=low (n=2)")
            )
          ) +
  labs(x="Time to Recurrence (Days)", y="Time to Recurrence probability")  +
  guides(col=guide_legend(nrow=4,byrow=TRUE))

@@

## COXPH ----
fit <- coxph(Surv(Time.to.reccurence..days., status) ~ sex + ASAH1.ng.ml + SYNM.ng.ml + GPNMB.ng.ml + MMP.9.ng.ml, data = ttr_surv_data)
print(summary(fit))
